---
title: "Causal Inference with R-CausalKit"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width  = 6,
  fig.height = 4
)
library(tidyverse)
library(MatchIt)
library(cobalt)
library(survey)
library(drtmle)
library(SuperLearner)
```

# 1. Simulate Data

```{r simulate-data}
source("../scripts/01_simulate_data.R")
glimpse(df)
```

# 2. Exploratory Data Analysis

```{r eda-density}
source("../scripts/02_eda_balance.R")
```

# 3. Propensity Score Matching

```{r psm}
source("../scripts/03_matchit_psm.R")
```

# 4. Inverse Probability Weighting

```{r ipw}
source("../scripts/04_ipw.R")
```

# 5. Doubly-Robust TMLE

```{r drtmle}
source("../scripts/05_drtmle_dr.R")
```

# 6. Summary & Conclusions

Summarize your findings here:
- How did naïve vs matched vs weighted vs DR estimates compare?
- Which method would you recommend, under what assumptions?
- Potential extensions (e.g., covariate interactions, Bayesian methods, Shiny dashboard).
